Review: Crop adaptation through post-domestication introgression from the wild

### 2016-05-24 TiG_prospectus.tex
edits to prospectus

The traditional paradigm in crop domestication studies has been origin from one or more defined geographic centers followed by dispersal and expansion to the modern-day extent of cultivation.
Absent from this paradigm are the genetic effects of hybridization between diffusing domesticates and closely-related, locally-adapted wild relatives outside the center of origin.
New methods have recently been employed to detect genome-wide patterns of introgression in a number of species.
In this review, we will: 1) briefly describe these methods and provide a summary of their recent application for detection of crop-wild introgression, 2) review evidence supporting the hypothesis that introgression has conferred local adaptation to crops, 3) consider how the prevalence of post-domestication introgression alters traditional concepts of domestication, and 4) describe future advances in basic and applied genetics that can be made through the study of crop-wild introgression.

@@

\section*{The role of introgression in conferring local adaptation in crops}

>>>>

The traditional paradigm in crop domestication studies has been origin from a wild relative within one or more defined geographic centers followed by dispersal and expansion to the modern-day extent of cultivation.
Absent from this paradigm are the effects of hybridization between diffusing domesticates and closely-related, locally-adapted wild relatives outside the center of origin.
New methods have recently been employed to detect genome-wide patterns of introgression in a number of species.
In this review, we will: 1) briefly describe these methods and provide a summary of their recent application for detection of crop-wild introgression, 2) review evidence supporting the hypothesis that wild-to-crop introgression has conferred local adaptation to crops, 3) consider how the prevalence of this introgression alters traditional concepts of domestication, and 4) describe future advances in both basic and applied genetics that can be made through the study of introgression in agroecosystems.

@@

\section*{The role of introgression in conferring local adaptation to crops}
